The \dealii Library, Version 9.0

### 2018-05-14 9.0/paper.tex
Rewrap some text.
The previous version spilled into the margins.

\item Improved support for user-defined run-time parameters: a new \texttt{ParameterAcceptor}
  class has been added to the library. The class is intended to be used as a
  base for any class that wants to handle parameters using the
  \texttt{ParameterHandler} class. If you derive all your classes from
  \texttt{ParameterAcceptor}, and declare your parameters either with
  \texttt{parse/declare\_parameters} methods or via the
  \texttt{ParameterAcceptor::add\_parameter} method, then both the
  declaration and the
  parsing of parameter files are automatically managed by
  \texttt{ParameterAcceptor::initialize}, greatly simplifying
  dealing with parameters in user codes.

>>>>

\item Improved support for user-defined run-time parameters: A new class
  \texttt{ParameterAcceptor} has been added to the library. Users should write
  classes inheriting from that class to manage parameters stored by a
  \texttt{ParameterHandler}. If the managing class is derived from
  \texttt{ParameterAcceptor} and all parameters are declared by either
  \texttt{parse\_parameters} and \texttt{declare\_parameters} or
  \texttt{ParameterAcceptor::add\_parameter}, then both the declaration and
  parsing of parameter files will be (instead of using ad-hoc calls to
  \texttt{ParameterHandler} methods) automatically managed by the
  \texttt{ParameterAcceptor::initialize} method, which greatly simplifies
  parameter management in user codes.
